Deterministic Scheduling of Periodic Messages for Cloud RAN

### 2017-07-28 infocom/infocom.tex

Let us expose briefly our model: the network topology is modeled by a directed weighted graph and a set of paths (routes) from source nodes (RRHs) to target nodes (BBUs). Time is discretized and a unit of time or slot corresponds to the transmission of a minimal unit of data over the network. The process must be  predictable (i.e. the date of arrival of packets is known beforehand). Following LTE standard~\cite{bouguen2012lte}, in this article we assume that the process is periodic. That is, if we look at the network at times $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network. We want to avoid any  buffering in internal nodes of the graph, hence we need to design a periodic process with no collisions between messages. To ensure that this property is always true we propose a deterministic process.  We have two sets of values that we can set when building a periodic sending process, called a \emph{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH. When building a periodic assignment, we must take into account the periodicity which makes many scheduling methods unusable. Not only a message must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods. The latency, that is the time between the emission of a message and the complete return of its answer must be minimized. This means that the only buffering we are allowed -- the waiting time before sending back the answer-- must be small, in particular when the route is long. Note that the model is technology agnostic, i.e. it is compatible with an optical network with a fixed packet size.

>>>>

Let us expose briefly our model: the network topology is modeled by a directed weighted graph and a set of paths (routes) from source nodes (RRHs) to target nodes (BBUs). Time is discretized and a unit of time or slot corresponds to the transmission of a minimal unit of data over the network. The process must be  predictable (i.e. the date of arrival of packets is known beforehand). Following LTE standard~\cite{bouguen2012lte}, in this article we assume that the process is periodic. That is, if we look at the network at times $t$ and $t+P$ where $P$ is the period, all messages are at the same position in the network. As we want to avoid any  buffering in internal nodes of the graph. Hence we need to design a periodic process with no collision between messages. To ensure that this property is always true we propose a deterministic process.  We have two sets of values that we can set when building a periodic sending process, called a \emph{periodic assignment} in this article: the time at which each packet is sent by a RRH in each period and the waiting time in the BBU before the answer is sent back to the RRH. When building a periodic assignment, we must take into account the periodicity which makes many scheduling methods unusable. Not only a message must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods. The latency, that is the time between the emission of a message and the complete return of its answer must be minimized. This means that the only buffering we are allowed -- the waiting time before sending back the answer-- must be small, in particular when the route is long. Note that the model is technology agnostic, i.e. it is compatible with an optical network with a fixed packet size.   
\renewcommand{\thefootnote}{\*}
\footnote{\href{https://1drv.ms/b/s!Aj8RtTXKWFgpgy9SiBowQNfvH-r9}{Please click here to download an extended version with details of mathematical proofs.}}
